PoPoolation Pipeline

### 2022-01-28 poolseq.Rmd
fixing Refs

---
title: "PoPoolation Pipeline"
subtitle: '*Joanna Griffiths*'
date: "8/12/2021"
#output:
#  html_document: default
#  pdf_document: default
#  word_document: default
---

@@

The following scripts were used to analyze data from an experimental evolution study on *Tigriopus californicus* copepods (Griffiths JS, Kawji Y, Kelly MW. 2020. An experimental test of adaptive introgression in locally adapted populations of splash pool copepods. Mol Biol and Evol. 38(4):1306-1316. https://doi.org/10.1093/molbev/msaa289). Raw sequencing data are deposited in NCBI's Short Reads Archive (https://www.ncbi.nlm.nih.gov/bioproject/PRJNA597336/). To download this dataset, go to: https://trace.ncbi.nlm.nih.gov/Traces/sra/sra.cgi?view=run_browser , then type in the accession number for the identified files you want to download (e.g., the accession no. for the file Bodega population file is SRR10760095, identified under the "Run" heading). Then click on the "Data access" tab, and there will be a downloadable link. Additional analyses and scripts can be found at: https://github.com/JoannaGriffiths/Tigriopus_HER

@@

Reference: Schlötterer C, Tobler R, Kofler R, Nolte V. 2014 Sequencing pools of individuals-mining genome-wide polymorphism data without big funding. Nat. Rev. Genet. 15, 749–763. (doi:10.1038/nrg3803)

@@

>>>>

---
title: "PoPoolation Pipeline"
subtitle: '*Joanna Griffiths*'
date: "8/12/2021"
bibliography: RCN_site-Nov05.bib
#output:
#  html_document: default
#  pdf_document: default
#  word_document: default
---

@@

The following scripts were used to analyze data from an experimental evolution study on *Tigriopus californicus* copepods (Griffiths 2020). Raw sequencing data are deposited in NCBI's Short Reads Archive (https://www.ncbi.nlm.nih.gov/bioproject/PRJNA597336/). To download this dataset, go to: https://trace.ncbi.nlm.nih.gov/Traces/sra/sra.cgi?view=run_browser , then type in the accession number for the identified files you want to download (e.g., the accession no. for the file Bodega population file is SRR10760095, identified under the "Run" heading). Then click on the "Data access" tab, and there will be a downloadable link. Additional analyses and scripts can be found at: https://github.com/JoannaGriffiths/Tigriopus_HER

@@

@@

## References
